---
title: "README"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
params:
  pkg: sglOptim
---

```{r, echo = FALSE}
set.seed(150)
pkg_version <- packageVersion(params$pkg)
```

## Sparse Group Lasso Solver

This is the R package sglOptim version **`r pkg_version`**.

### R-package Overview

This package doesn't provide any direct functionality. It is a service package 
for other R packages, and it provides an implementation of an optimizer of 
sparse group lasso penalized objective functions. The package is used 
by the following other R packages:

* For fitting **multivariate linear regression** models using sparse group lasso see the [lsgl](https://github.com/nielsrhansen/lsgl) R package.
* For fitting **multinomial classification models** using sparse group lasso see the [msgl](https://github.com/nielsrhansen/msgl) R package.

More details on the algorithm are given in the paper [Sparse group lasso and high dimensional multinomial classification](http://dx.doi.org/10.1016/j.csda.2013.06.004). 


The loss/objective function must be defined in a C++ module.

### Installation

Install the released version from CRAN:

```{r eval = FALSE}
install.packages("sglOptim")
```

Install the version from GitHub:

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("nielsrhansen/sglOptim", build_vignettes = TRUE)
```


If you don't want to build the vignettes when installing, just remove the 
`build_vignettes = TRUE` argument.

### Author

Martin Vincent wrote the package. Niels Richard Hansen is the current maintainer.

### License

GPL (>=2)
