---
title: "README"
author: "Martin Vincent"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
params:
  pkg: sglOptim
---

```{r, echo = FALSE}
set.seed(150)

pkg_version <- packageVersion(params$pkg)

x_dcf <- read.dcf(file = file.path(getwd(), "..", "DESCRIPTION"))

if("GitHubRepo" %in% colnames(x_dcf)) {
  pkg_branch <- x_dcf[1,"GitHubRepo"]

  pkg_version_type <- switch(pkg_branch,
    release = "release",
    master = "release candidate",
    develop = "development version"
  )
} else {
  pkg_branch <- "release"
  pkg_version_type <- "release"
}
```

## Sparse Group Lasso Solver

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/`r params$pkg`)](https://cran.r-project.org/package=`r params$pkg`)
[![Travis-CI Build Status](https://travis-ci.org/vincent-dk/`r params$pkg`.svg?branch=`r pkg_branch`)](https://travis-ci.org/vincent-dk/`r params$pkg`)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/vincent-dk/`r params$pkg`?branch=`r pkg_branch`&svg=true)](https://ci.appveyor.com/project/vincent-dk/`r params$pkg`)
[![Coverage Status](https://codecov.io/github/vincent-dk/`r params$pkg`/coverage.svg?branch=`r pkg_branch`)](https://codecov.io/github/vincent-dk/`r params$pkg`?branch=`r pkg_branch`)

This is the **`r pkg_version_type`** of R package **`r params$pkg` version `r pkg_version`**.

### R-package Overview

This package is not intended for direct use, it is a service package for other R packages.
If you want to use the optimizer I recommend you do one of the following:

* To make a **custom sparse group lasso package** (i.e. implement your own loss/objective function) see the GitHub repo [Xsgl](https://github.com/vincent-dk/Xsgl) and documentation therein.
* For fitting **linear multiple output** models using sparse group lasso see the [lsgl](https://github.com/vincent-dk/lsgl) R-package.
* For doing **multi-class classification** using sparse group lasso see the [msgl](https://github.com/vincent-dk/msgl) R-package.
* For doing **multi-label logistic regression** using sparse group lasso see the [logitsgl](https://github.com/vincent-dk/logitsgl) R-package.

For details on the algorithm and more see <http://dx.doi.org/10.1016/j.csda.2013.06.004>. The loss/objective function must be defined in a C++ module, for more information see [Building a Customized Sparse Group Lasso Package](https://vincent-dk.github.io/docs/Xsgl_docs/build_sgl_package.html).

### Installation

Install the released version from CRAN:

```{r eval = FALSE}
install.packages("sglOptim")
```

Install the release candidate from GitHub:

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("vincent-dk/sglOptim")
```

Install the development version from GitHub:

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("vincent-dk/sglOptim", ref = "develop")
```

### Author

Martin Vincent

### License

GPL (>=2)
